---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(dplyr)
library(stringr)
library(fs)
library(here)
library(glue)
library(readr)
```

A repository of [AACT](https://aact.ctti-clinicaltrials.org/) data for trials affiliated with several Californian universities.

```{r queries, echo = FALSE}

loggit::read_logs(here::here("queries.log")) %>% 
  filter(str_detect(log_msg, "AACT")) %>% 
  group_by(log_msg) %>% 
  slice_tail(n = 1) %>% 
  ungroup() %>% 
  summarise(
    organization = str_remove(log_msg, "AACT_"),
    query_date = as.Date.character(timestamp)
  ) %>% 
  knitr::kable()

```

Tidied csv's are available in `data --> processed --> {organization}`:

-   `{organization}_studies.csv` includes all trials from AACT affiliated with {organization}
-   `{organization}_trials.csv` is limited to interventional trials completed in or before 2020 with relevant status: "Completed" , "Terminated" , "Suspended", "Unknown status"

## Sample to match Chen et al. (2016)

In order to develop samples to match Chen et al. (2016), we apply the following criteria to `{organization}_studies.csv`:

-   interventional
-   overall_official from {organization} ("To identify trials with the responsible party based at an academic medical center, we selected those affiliated with an academic medical center, using the 'role' field to identify the lead investigator, and his or her primary affiliation through the 'affiliation' field.")
-   primary completion date within specified range
-   exclude "Unknown status" & "Withdrawn" ("We identified and excluded clinical trials with an unknown or withdrawn status")

Csv's are available in `data --> processed --> {organization} --> {organization}-trials-chen-20XX-20XX.csv`

Below is a comparison of trials in Chen 2007-2010 and our sample, for 2007-2010 and 2014-2017.
Note that discrepancies are expected due to differences in dates: Chen and colleagues include trials with a primary completion date between "October 2007 and September 2010," whereas we use all of 2007 through all of 2010. Furthermore, it is likely some registrations had data changed since Chen's data extraction.

```{r chen, echo = FALSE, message = FALSE}

dir_processed <- here("data", "processed")

our_trials <-
  dir_ls(dir_processed) %>%
  path_file() %>%
  path_ext_remove() %>% 
  tibble::as_tibble_col(column_name = "university") %>% 
  rowwise() %>% 
  mutate(n_trials_2007_2010 = nrow(read_csv(glue("{dir_processed}/{university}/{university}-trials-chen-2007-2010.csv")))) %>% 
    mutate(n_trials_2014_2017 = nrow(read_csv(glue("{dir_processed}/{university}/{university}-trials-chen-2014-2017.csv")))) %>% 
  ungroup()

chen_trials <- tribble(
  ~university, ~n_trials_chen_2007_2010,
  "stanford", 131,
  "ucdavis", 64,
  "uci", 42,
  "ucla", 95,
  "ucsd", 75,
  "ucsf", 133
)

chen_vs_our_trials <- full_join(chen_trials, our_trials)

knitr::kable(chen_vs_our_trials)
```

## References

Chen, R., Desai, N. R., Ross, J. S., Zhang, W., Chau, K. H., Wayda, B., Murugiah, K., Lu, D. Y., Mittal, A., & Krumholz, H. M. (2016). Publication and reporting of clinical trial results: Cross sectional analysis across academic medical centers. *BMJ*, *352*. <https://doi.org/10.1136/bmj.i637>
