---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(dplyr)
library(stringr)
```

A repository of [AACT](https://aact.ctti-clinicaltrials.org/) data for trials affiliated with several Californian universities.

```{r queries, echo = FALSE}

loggit::read_logs(here::here("queries.log")) %>% 
  filter(str_detect(log_msg, "AACT")) %>% 
  group_by(log_msg) %>% 
  slice_tail(n = 1) %>% 
  ungroup() %>% 
  summarise(
    organization = str_remove(log_msg, "AACT_"),
    query_date = as.Date.character(timestamp)
  ) %>% 
  knitr::kable()
  
```

Tidied csv's are available in `data --> processed --> {organization}`:

-   `{organization}_studies.csv` includes all trials from AACT affiliated with {organization}
-   `{organization}_trials.csv` is limited to interventional trials completed in or before 2020 with relevant status: "Completed" , "Terminated" , "Suspended", "Unknown status"
